Multisensor Architecture for an Intersection Management System

### 2018-02-22 ch3-arch_sys.tex
Updated data model section

---TODO: Describe and add UML of classes --
-- describe intersection model
--Describe data from flow

>>>>

---TODO: Describe and add UML of classes --

The intersection has been modeled as a class with attributes like a label, a Map object, a set of RangeSensors and CameraSensors objects, a set of Leg objects, and a set of Area objects, for inner area of the intersection. The Map class contains information about the geometry of the intersection and the coordinate system, including a image intended for visualization of configuration and processing.

The sensors sets are composed of zero or more sensor objects, as defined previously. An Area class is defined as having a bounding box and a label	. From this class, a derived class Leg is defined for containing additional information about the legs of the intersection, such as heading of the leg, approaching or departure type.

The purpose of all the labels attributes within each class is to serve as an identifier of the channel in which the entity is publishing or subscribing.
-- describe intersection model
--Describe data from flow
